Constraining the Interiors of Asteroids Through Close Encounters

### 2022-03-29 paper/main.tex
Ready to run blob

For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic). However, the two models do give similar results. Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case does indeed place more mass in the center of the asteroid shape for the harmonic and likelihood models. The edge-weighted asteroid does not have as clear high-density at its surface, due to the fact that uncertainty is generally greater near the edges (where $R_{\ell m}$ is large).

\jtd{Rewrite after new model comes through}

>>>>

For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic). However, the two models do give similar results. Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case indeed places more mass in the center of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.

Though the general mass placement arrived at by both the likelihood and harmonic models is accurate, the precise density distributions are inaccurate because they predict negative densities. This might be addressed for the likelihood model by selecting a likelihood that strongly disfavors negative densities, such as a log-normal distribution. However, this would sacrifice the linearity of the model, so we do not do so here, accepting the fact that for strongly varying distributions, the harmonic and likelihood models may predict negative density distributions.

Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the center-weighted asteroid and less density for the edge-weighted asteroid, as expected. Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models. Note that the lumpy model predicts negative density in the the edge-weighted scenario like the other two models.
